Location and Scale-Invariant Power Transformations for Transforming Data to Normality

### 2025-10-29 manuscript_latex/manuscript.tex
Update appendix C

\section{Central normality test and empirical central
normality test critical
values}\label{appendix-c}

Critical values for the central normality test and its empirical variant
are found in Table \ref{tab:central-normality-critical-statistic} and
Table \ref{tab:empirical-central-normality-critical-statistic},
respectively.

\begin{table}
\caption{Critical values of test statistic $\tau_{\alpha, n, \kappa = 0.80}$ for
\textbf{central normality} at $\kappa = 0.80$, as a function of significance
level $\alpha$ and number of instances $n$. The values shown must be divided by $100$.}
\label{tab:central-normality-critical-statistic}
\begin{tabular}{l | r r r r r r r r r}

@@

\midrule
    5 & 210.79 & 95.75 & 66.27 & 49.69 & 35.93 & 27.60 & 19.29 & 13.41 & 11.00 \\
   10 &  48.04 & 31.44 & 26.96 & 23.91 & 21.11 & 18.16 & 13.66 & 10.14 &  8.67 \\
   20 &  29.13 & 22.13 & 19.75 & 17.94 & 16.00 & 13.81 & 10.54 &  8.18 &  7.18 \\
   50 &  17.31 & 14.01 & 12.63 & 11.48 & 10.28 &  9.00 &  7.00 &  5.54 &  4.94 \\
  100 &  12.19 & 10.04 &  9.02 &  8.21 &  7.38 &  6.47 &  5.04 &  3.99 &  3.56 \\
  200 &   8.68 &  7.11 &  6.40 &  5.83 &  5.22 &  4.57 &  3.59 &  2.86 &  2.56 \\
  500 &   5.61 &  4.54 &  4.08 &  3.70 &  3.33 &  2.91 &  2.28 &  1.82 &  1.63 \\
 1000 &   3.93 &  3.19 &  2.87 &  2.60 &  2.33 &  2.05 &  1.61 &  1.29 &  1.15 \\
 2000 &   2.71 &  2.24 &  2.02 &  1.84 &  1.66 &  1.46 &  1.14 &  0.91 &  0.82 \\
 5000 &   1.73 &  1.42 &  1.28 &  1.17 &  1.05 &  0.92 &  0.72 &  0.58 &  0.52 \\
10000 &   1.22 &  1.00 &  0.90 &  0.82 &  0.74 &  0.65 &  0.51 &  0.41 &  0.37 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\caption{Critical values of test statistic $\tau_{\alpha, n, \kappa = 0.70}$ for
\textbf{empirical central normality} at $\kappa = 0.70$, as a function of significance
level $\alpha$ and number of instances $n$. The values shown must be divided by $100$.}
\label{tab:empirical-central-normality-critical-statistic}
\begin{tabular}{l | r r r r r r r r r}

\midrule
    5 & 159.27 & 66.78 & 57.06 & 50.55 & 43.42 & 34.89 & 22.28 & 14.92 & 12.10 \\
   10 &  41.82 & 30.82 & 27.01 & 24.31 & 21.58 & 18.53 & 13.82 & 10.23 &  8.75 \\
   20 &  29.44 & 23.65 & 21.23 & 19.16 & 17.01 & 14.67 & 11.10 &  8.42 &  7.35 \\
   50 &  18.95 & 15.56 & 13.96 & 12.74 & 11.35 &  9.82 &  7.51 &  5.83 &  5.16 \\
  100 &  13.49 & 11.00 &  9.91 &  8.98 &  8.03 &  7.04 &  5.43 &  4.25 &  3.76 \\
  200 &   9.65 &  7.99 &  7.22 &  6.64 &  5.96 &  5.21 &  4.05 &  3.17 &  2.81 \\
  500 &   6.37 &  5.32 &  4.82 &  4.44 &  4.03 &  3.57 &  2.79 &  2.18 &  1.92 \\
 1000 &   4.64 &  3.95 &  3.65 &  3.39 &  3.11 &  2.78 &  2.20 &  1.73 &  1.53 \\
 2000 &   3.61 &  3.18 &  2.96 &  2.78 &  2.57 &  2.32 &  1.89 &  1.50 &  1.33 \\
 5000 &   2.78 &  2.48 &  2.36 &  2.24 &  2.11 &  1.95 &  1.66 &  1.39 &  1.25 \\
10000 &   2.39 &  2.18 &  2.08 &  2.00 &  1.91 &  1.81 &  1.59 &  1.39 &  1.28 \\
\bottomrule
\end{tabular}
\end{table}

{\centering \includegraphics[width=1\linewidth]{appendix_figure_2}

\caption{Critical test statistic $\tau_{\alpha, n, \kappa = 0.80}$ of the (empirical) central normality test as function of $n$ for several values of significance level $\alpha$. The critical test statistics for central normality test are determined using fully normal data, whereas the statistics for the empirical variant are determined using centrally normal data, i.e. with fully normal data where 10\% of elements are replaced by outliers. emp: empirical}\label{fig:empirical-central-normality-critical-statistics}
\end{figure}

>>>>

\section{Appendix C: Empirical central normality test critical values}
\label{appendix-c}

Critical values for the empirical central normality test at
\(\kappa = 0.80\) are found in Table
\ref{tab:empirical-central-normality-critical-statistic}.

\begin{table}
\begin{center}
\caption{Critical values of test statistic $\tau_{\alpha, n, \kappa = 0.80}$ for
central normality at $\kappa = 0.80$, as a function of significance
level $\alpha$ and number of instances $n$. The values in this table should be divided by $100$ before use.}
\label{tab:empirical-central-normality-critical-statistic}
\begin{tabular}{l | r r r r r r r r r}

@@

\midrule
    5 & 200.88 & 90.25 & 64.46 & 49.04 & 36.07 & 27.70 & 19.28 & 13.41 & 10.90 \\
   10 &  45.90 & 31.78 & 27.12 & 24.14 & 21.23 & 18.30 & 13.68 & 10.20 &  8.71 \\
   20 &  28.88 & 22.53 & 19.96 & 18.01 & 15.99 & 13.93 & 10.67 &  8.26 &  7.27 \\
   50 &  16.86 & 14.10 & 12.66 & 11.55 & 10.28 &  8.95 &  7.00 &  5.53 &  4.91 \\
  100 &  12.41 & 10.00 &  9.02 &  8.21 &  7.36 &  6.45 &  5.02 &  4.00 &  3.58 \\
  200 &   8.65 &  7.05 &  6.37 &  5.80 &  5.22 &  4.57 &  3.57 &  2.84 &  2.54 \\
  500 &   5.54 &  4.47 &  4.03 &  3.69 &  3.30 &  2.90 &  2.27 &  1.81 &  1.63 \\
 1000 &   3.88 &  3.17 &  2.86 &  2.60 &  2.34 &  2.05 &  1.61 &  1.28 &  1.15 \\
 2000 &   2.79 &  2.24 &  2.03 &  1.84 &  1.66 &  1.45 &  1.14 &  0.91 &  0.82 \\
 5000 &   1.75 &  1.41 &  1.27 &  1.17 &  1.05 &  0.92 &  0.72 &  0.58 &  0.52 \\
10000 &   1.21 &  1.00 &  0.90 &  0.82 &  0.74 &  0.65 &  0.51 &  0.41 &  0.36 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}
